% This template is a modified version of one
% downloaded from a free templates website.
% Original documentation perserved below:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Kelly Sovacool} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

%\moveleft.5\hoffset\centerline{123 Broadway} % professional / academic address
%\moveleft.5\hoffset\centerline{City, State 12345}
%\moveleft.5\hoffset\centerline{(000) 111-1111 or (111) 111-1112}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

%\section{OBJECTIVE}

% text goes here

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Bachelor of Science,} Biology \hfill 2014-2018 \\
University of Kentucky, Lexington, KY \\
Minor: Computer Science
\begin{itemize} \itemsep -2pt % Reduce space between items
\item 4-year Full Tuition Presidential Scholarship
\item Lewis Honors College
\item Honors Biology Scholar
\end{itemize}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{RESEARCH}

{\sl Undergraduate Lab Assistant} \hfill 2015-present \\
Moseley Bioinformatics Lab, Dept. of Molec. \& Cell. Biochemistry, University of Kentucky
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developing a computational tool for identifying sets of orthologous and paralogous gene products across any set of whole genomes to facilitate collinearity analysis and detection of gene duplication events.
\end{itemize}

{\sl BIO395 Independent Research Student} \hfill 2016-present \\
Weisrock Lab, Dept. of Biology, University of Kentucky
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Population structure analysis of the {\sl Ambystoma} tiger salamander complex.
\item Bayesian species delimitation of the {\sl Desmognathus} dusky salamander complex.
\item Writing Bash and Python scripts for managing sequence data.
\item Developing a SNP calling pipeline for amplicon sequence data
\end{itemize}

{\sl Undergraduate Lab Assistant} \hfill 2015-2016 \\
Jaromczyk Lab, Dept. of Computer Science, University of Kentucky
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Maintained the E. festucae genome project database.
\item Applied methods of processing RNA-seq data to {\sl C. quinoa} and the Coffee ringspot virus.
\end{itemize}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{AWARDS}

{\sl Oswald Research \& Creativity Award} , University of Kentucky \hfill 2017
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Awarded a \$200 prize for second place in the Biological Sciences category.
\item Manuscript title: Developing a Global Homology and Collinearity Analysis Framework for Identifying Gene Duplication Events. Supervised by Prof. Hunter NB Moseley.
\end{itemize}

{\sl Summer Research Grant,}  University of Kentucky \hfill 2017
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Awarded a \$2,000 grant by the UK Office of Undergraduate Research to work full time on a research project during the summer.
\item Project title: Developing a Global Homology and Collinearity Analysis Framework for Identifying Gene Duplication Events. Supervised by Prof. Hunter NB Moseley.
\end{itemize}

%----------------------------------------------------------------------------------------
%   PRESENTATIONS SECTION
%----------------------------------------------------------------------------------------

\section{POSTERS \& ORALS} % the word "PUBLICATIONS" was too long and ran into the title of the first one :(

{\sl Developing a Global Homology Analysis Framework for Comparative Genomics} \\
Supervised by Prof. Hunter NB Moseley.
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Poster presented at the Showcase of Undergraduate Scholars, University of Kentucky. April 25, 2018.
\item Oral presentation given at the Systems Biology \& Omics Integration Seminar Series, University of Kentucky. April 16, 2018.
\item Poster presented at the National Conference on Undergraduate Research, University of Central Oklahoma. April 4-7, 2018.
\end{itemize}

{\sl Processing RNA-seq Reads of Plants Infected with the Coffee Ringspot Virus} \\
Supervised by Profs. Jerzy W Jaromczyk and Michael M Goodin.
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Poster presented at the Showcase of Undergraduate Scholars, University of Kentucky. April 27, 2016.
\item Poster presented at the UT-KBRIN Bioinformatics Summit, Cadiz, KY. April 8-10, 2016.
\end{itemize}

{\sl The Effect of Meditation on Performance} \\
Supervised by Prof. Bruce O’Hara.
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Poster presented at the Showcase of Undergraduate Scholars, University of Kentucky. April 29, 2015
\end{itemize}

%----------------------------------------------------------------------------------------
%   OTHER WORK SECTION
%----------------------------------------------------------------------------------------

\section{OTHER WORK}

{\sl Tutor} \hfill 2012-2017
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Tutored high school and college students in Biology, Calculus, Chemistry, Computer Science, and Bioinformatics.
\end{itemize}

{\sl Sound Technician} \hfill 2009-present
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Setting up, maintaining, repairing, and operating audio equipment for bands, churches, and other non-profit organizations.
\item Operating the front of house, monitor, and recording systems during sound checks, rehearsals, services, and concerts.
\item Training new sound techs in the art and science of live sound.
\end{itemize}

%----------------------------------------------------------------------------------------
\end{resume}
\end{document}
