% This template is a modified version of `template-multibib.tex`
% downloaded from the moderncv repo: https://github.com/xdanaux/moderncv
% Original documentation preserved below:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[12pt,sans,colorlinks,linkcolor=true]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{black}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage{textcomp,xpatch}
\xpatchcmd{\cventry}{\itshape#3}{#3}{}{} % Patch \cventry so the 3rd argument is not printed in italics
\xpatchcmd{\cventry}{.\strut}{\strut}{}{} % Patch \cventry to remove the trailing period
% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex,
\usepackage[scale=0.75]{geometry} % adjust the page margins
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Kelly L. Sovacool}{}
%\title{Resumé title}
%\address{street and number}{postcode city}{country}% the "postcode city" and "country" arguments can be omitted or provided empty
%\phone[mobile]{+1~(234)~567~890}                   %  the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{sovacool@umich.edu}
\homepage{sovacool.dev}
\social[linkedin]{kelly-sovacool}
%\social[xing]{john\_doe}
\social[twitter]{kelly-sovacool}
\social[github]{kelly-sovacool}
%\social[gitlab]{jdoe}
%\social[skype]{jdoe}
%\extrainfo{additional information}
%\photo[64pt][0.4pt]{picture}                       %  '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
%\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
% default bibliography
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\definecolor{links}{HTML}{0000FF}  % color url links blue
\hypersetup{urlcolor=links}
\makecvtitle

\section{Education}

\cventry{2018-present}{PhD Student - Bioinformatics}{University of Michigan}{\newline Dept. of Computational Medicine and Bioinformatics}{\newline Medical School | Rackham Graduate School}{Advisor: Pat Schloss}

\cventry{2014-2018}{BS Biology}{University of Kentucky}{}{}{
\begin{itemize}
\item Minor: Computer Science
\item 4-year full tuition Presidential Scholarship
\item Graduated Cum Laude
\item Departmental Honors in Biology
\item Lewis Honors College
\end{itemize}}

%----------------------------------------------------------------------------------

\section{Research Experience}

\cventry{2019-present}{Graduate Student Research Assistant}{\href{www.schlosslab.org}{Schloss Lab}}{\newline Dept. of Microbiology and Immunology}{University of Michigan}{
\begin{itemize}
    \item Developing bioinformatics tools \& pipelines for microbial ecology.
    \item 16S rRNA sequence analysis and tandem mass spectrometry data analysis.
\end{itemize}
}
\cventry{2018-2019}{Rotation Student Researcher}{Program in Biomedical Sciences}{\newline University of Michigan}{}{%Conducted research in the labs of Arvind Rao, Pat Schloss, Lana Garmire, and Muneesh Tewari as a first-year PhD student.
\begin{itemize}
    \item Arvind Rao lab: identifying master transcription factors in glioma progression.
    \item Pat Schloss lab: benchmarking clustering algorithms for microbiome research.
    \item Lana Garmire lab: characterizing lncRNA variation across cancer types.
    \item Muneesh Tewari lab: exploring the miRNA profiles of healthy individuals.
\end{itemize}
}
\cventry{2015-2018}{Undergraduate Lab Assistant}{\href{http://bioinformatics.cesb.uky.edu/}{Moseley Bioinformatics Lab}}{\newline Dept. of Molecular and Cellular Biochemistry}{University of Kentucky}{
\begin{itemize}
\item Developed a computational tool for identifying sets of orthologous and \allowbreak paralogous gene products in whole genomes to facilitate collinearity analysis and detection of gene duplication events.
\end{itemize}
}
\cventry{2016-2018}{BIO395 Independent Research Student}{\href{http://sweb.uky.edu/~dweis2/The_Weisrock_Lab}{Weisrock Lab}}{\newline Dept. of Biology}{University of Kentucky}{
\begin{itemize}
\item Developed scripts and a SNP calling pipeline for amplicon sequence data.
\item Population structure analysis of the \textit{Ambystoma tigrinum} species complex.
\item Bayesian species delimitation of the \textit{Desmognathus fuscus} species complex.
\end{itemize}
}
\cventry{2015-2016}{Undergraduate Lab Assistant}{\href{http://csurs.csr.uky.edu/}{Jaromczyk Lab}}{\newline Dept. of Computer Science}{University of Kentucky}{
\begin{itemize}
\item Maintained the \textit{Epichloë festucae} genome project database.
\item Analyzed RNA-seq data of \textit{Chenopodium quinoa} and coffee ringspot virus.
\end{itemize}
}
%----------------------------------------------------------------------------------
%\pagebreak
\section{Awards}

\cventry{Dec 2017}{Oswald Research \& Creativity Award}{\mdseries University of Kentucky}{}{}{
\begin{itemize}
\item Awarded a \$200 prize for second place in the Biological Sciences category.
\item Manuscript title: "Developing a Global Homology and Collinearity Analysis Framework for Identifying Gene Duplication Events."
\item Advisor: Prof. Hunter NB Moseley.
\end{itemize}
}
\cventry{May 2017}{Summer Research Grant}{\mdseries University of Kentucky}{}{}{
\begin{itemize}
\item Awarded a \$2,000 grant by the UK Office of Undergraduate Research to work full time on a research project during the summer.
\item Project title: "Developing a Global Homology and Collinearity Analysis \allowbreak Framework for Identifying Gene Duplication Events."
\item Advisor: Prof. Hunter NB Moseley.
\end{itemize}}

%----------------------------------------------------------------------------------

\section{Presentations}

\cventry{Apr 2018}{Developing a Global Homology Analysis for Comparative Genomics}{Advisor: Prof. Hunter NB Moseley}{}{}{
\begin{itemize}
\item Poster, \textit{Showcase of Undergraduate Scholars}, University of Kentucky
\item Oral, \textit{Systems Biology \& Omics Integration Seminar}, University of Kentucky
\item Poster, \textit{National Conference on Undergraduate Research}, University of Central Oklahoma
\end{itemize}
}
\cventry{Apr 2016}{Processing RNA-seq Reads of Plants Infected with the Coffee Ringspot Virus}{Advisor: Prof. Jerzy W Jaromczyk}{}{}{
\begin{itemize}
\item Poster, \textit{Showcase of Undergraduate Scholars}, University of Kentucky
\item Poster, \textit{UT-KBRIN Bioinformatics Summit}, Cadiz, KY
\end{itemize}
}
\cventry{Apr 2015}{The Effect of Meditation on Performance}{Advisor: Prof. Bruce O’Hara}{}{}{
\begin{itemize}
\item Poster, \textit{Showcase of Undergraduate Scholars}, University of Kentucky
\end{itemize}
}

%----------------------------------------------------------------------------------

\section{Service}

\cventry{2019-present}{Graduate Student Coordinator}{organize monthly meetings for researchers to sharpen their data analysis skills}{\href{https://um-dang.github.io}{Data Analysis Networking Group}}{}{University of Michigan}

\cventry{2019-present}{Executive Committee Member}{plan and develop curriculum for a weekly club teaching programming \& data science to high school women}{\href{http://umich.edu/~girlswc/}{Girls Who Code at UM-DCMB}}{}{University of Michigan}

\cventry{2018-present}{Summer Experience Committee Member}{plan, apply for funding, and develop curriculum for our \href{http://umich.edu/~girlswc/summer.html}{Data Science Summer Experience} for high school women in downtown Detroit}{\href{http://umich.edu/~girlswc/}{Girls Who Code at UM-DCMB}.}{}{University of Michigan}

\cventry{2009-present}{Live Sound Engineer}{\href{https://sovacool.dev/latex-cv/cv_sound_KLS.pdf}{for various churches and non-profit organizations}.}{}{}{
\begin{itemize}
\item Set up, maintain, repair, and operate front of house, monitor, and recording systems during sound checks, rehearsals, services, and concerts.
\item Train new sound techs in the art and science of live sound.
\end{itemize}
}

\section{Teaching Experience}

\cventry{15-19 July 2019}{Facilitator \& Mentor}{taught programming and guided high school women through a data science project and presentation during the \href{http://umich.edu/~girlswc/summer.html}{Data Science Summer Experience}}{\href{http://umich.edu/~girlswc/}{Girls Who Code at UM-DCMB}.}{}{Detroit, MI}

\cventry{01-02 July 2019}{Software Carpentry instructor}{\href{https://umswc.github.io/2019-07-1-umich/}{workshop} teaching the Unix Shell, version control with Git, and R programming.}{}{}{University of Michigan}

\cventry{22-23 May 2019}{Software Carpentry helper}{\href{https://davebridges.github.io/2019-05-23-shapiro/}{workshop} teaching the Unix shell, version control with Git, and Python programming.}{}{}{University of Michigan}

\cventry{25 Apr 2019}{DNA Day Ambassador}{taught an epigenetics lesson to high school biology students}{\href{https://midnaday.com/}{MI DNA Day}}{Pioneer High School}{Ann Arbor, MI}

\cventry{20 Mar 2019}{Workshop helper}{during GSBES meeting teaching \href{https://github.com/GWC-DCMB/codeDemos}{data visualization with Python}}{\href{https://maizepages.umich.edu/organization/gsbes}{Graduate Society of Black Engineers and Scientists}.}{}{University of Michigan}

\cventry{16 Mar 2019}{Capstone activity leader}{\href{https://github.com/GWC-DCMB/ozobotLessons}{taught binary numbers with Ozobots} at FEMMES capstone event for middle school students}{\href{https://www.femmes.studentorgs.umich.edu/}{Females Excelling More in Math, Engineering, \& Science}.}{}{University of Michigan}

\cventry{01 Mar 2019}{Software Carpentry helper}{\href{https://umswc.github.io/2019-02-28-umich/}{workshop} teaching the Unix shell, version control with Git, and Python programming.}{}{}{University of Michigan}

\cventry{Jan-May 2019}{Capstone project mentor}{guided high school women through a data science project and presentation}{\href{http://umich.edu/~girlswc/}{Girls Who Code at UM-DCMB}.}{}{University of Michigan}

\cventry{17-18 Dec 2018}{Software Carpentry helper}{\href{https://umswc.github.io/2018-12-17-umich/}{workshop} teaching the Unix shell, R programming, and version control with Git.}{}{}{University of Michigan}

\cventry{2012-2017}{Tutor}{for high school and college students in Biology, Calculus, Chemistry, Computer Science, and Bioinformatics.}{}{}{}




%----------------------------------------------------------------------------------

%\section{Teaching Experience}

%----------------------------------------------------------------------------------
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
% TODO: uncomment the below three lines when I have more publications
%\nocite{*} % allow everything in bibtex file that wasn't cited in-text to be included here
%\bibliographystyle{abbrv}
%\bibliography{cv_KLS} % cv_KLS.bib is a bibtex file with your publications

\end{document}
