%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 8 February 2019
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,]{moderncv}

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{HTML}{3873B3}% custom
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\usepackage[]{sans}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\def\donothing#1{#1}
\def\emaillink#1{#1}

%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75,footskip=60pt]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...


\moderncvcolor{black}

% UMich colors https://brand.umich.edu/design-resources/colors/
\definecolor{MichiganBlue}{HTML}{00274C}
\definecolor{RackhamGreen}{HTML}{75988d}
\definecolor{ArboretumBlue}{HTML}{2F65A7}
\definecolor{TaubmanTeal}{HTML}{00B2A9}
\definecolor{AngelHallAsh}{HTML}{989C97}
\definecolor{PumaBlack}{HTML}{131516}

% CUSTOM COLORS for moderncv
% https://tex.stackexchange.com/questions/109496/creating-additional-color-for-moderncv
\colorlet{color0}{PumaBlack}
\colorlet{color1}{MichiganBlue}
\colorlet{color2}{MichiganBlue}


\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage{textcomp,xpatch}
\xpatchcmd{\cventry}{\itshape#3}{#3}{}{} % Patch \cventry so the 3rd argument is not printed in italics
\xpatchcmd{\cventry}{.\strut}{\strut}{}{} % Patch \cventry to remove the trailing period

% quote width https://tex.stackexchange.com/questions/163050/how-can-i-extend-quotes-width-in-moderncv
\let\originalrecomputecvlengths\recomputecvlengths
\renewcommand*{\recomputecvlengths}{%
\originalrecomputecvlengths%
\setlength{\quotewidth}{0.99\textwidth}}

% personal data
\name{}{Kelly Sovacool}


 % Phone number
\email{\donothing{\href{mailto:sovacool@umich.edu}{\nolinkurl{sovacool@umich.edu}}}}
\homepage{sovacool.dev} % Personal website
\social[linkedin]{kelly-sovacool}

\social[github]{kelly-sovacool}
% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted




% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle



\hypersetup{urlcolor=ArboretumBlue}

\emph{Bioinformatician building and applying open source tools for
microbiome research, and contributing to data science education along
the way.}

\hypertarget{education}{%
\section{Education}\label{education}}

\nopagebreak
    \cventry{2018-present}{PhD Bioinformatics}{Dept. of Computational Medicine and Bioinformatics}{University of Michigan}{}{\begin{itemize}%
\item Advisor: Patrick D. Schloss%
\end{itemize}}
    \cventry{2014-2018}{BS Biology}{Dept. of Biology}{University of Kentucky}{}{\begin{itemize}%
\item Minor: Computer Science%
\end{itemize}}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\nopagebreak
    \cvitem{Languages \& Tools}{R, Python, Bash, C++, Snakemake, R Markdown, Quarto, LaTeX, conda, git, GitHub, SLURM. }
    \cvitem{Research}{gut microbiome composition, amplicon sequence analysis, metagenomics, supervised machine learning, data visualization, reproducible manuscripts. }
    \cvitem{Software}{R package maintenance, continuous integration, high performance computing. }

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\nopagebreak
    \cventry{2019-present}{Graduate Student Researcher}{Schloss Lab,  Dept. of Microbiology and Immunology}{University of Michigan}{}{\begin{itemize}%
\item Develop and benchmark bioinformatics pipelines and software for microbial ecology.%
\item Analyze 16S rRNA gene amplicon sequence data.%
\item Apply machine learning methods to gut microbiome classification problems in colorectal cancer and \_C. difficile\_ infection.%
\item Collaborate with other scientists on microbiome projects and mentor junior lab members.%
\end{itemize}}
    \cventry{2018-2019}{Rotation Student Researcher}{Program in Biomedical Sciences}{University of Michigan}{}{\begin{itemize}%
\item %
\end{itemize}}
    \cventry{2015-2018}{Undergraduate Lab Assistant}{Moseley Bioinformatics Lab,  Dept. of Molecular and Cellular Biochemistry}{University of Kentucky}{}{\begin{itemize}%
\item Developed a computational tool in Python for identifying sets of orthologous and paralogous gene products in whole genomes to facilitate collinearity analysis and detection of gene duplication events.%
\end{itemize}}
    \cventry{2016-2018}{BIO395 Independent Research Student}{Weisrock Lab,  Dept. of Biology}{University of Kentucky}{}{\begin{itemize}%
\item Developed bash scripts and a SNP calling pipeline in Snakemake.%
\item Population structure analysis of the \_Ambystoma tigrinum\_ species complex.%
\item Bayesian species delimitation of the \_Desmognathus fuscus\_ species complex.%
\end{itemize}}
    \cventry{2015-2016}{Undergraduate Lab Assistant}{Jaromczyk Lab,  Dept. of Computer Science}{University of Kentucky}{}{\begin{itemize}%
\item Maintained the \_Epichloë festucae\_ genome project database.%
\item Analyzed RNA-seq data of \_Chenopodium quinoa\_ and coffee ringspot virus.%
\end{itemize}}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\nopagebreak
    \cventry{Jan-Apr 2023}{Graduate Student Instructor}{Dept. of Computational Medicine \& Bioinformatics}{University of Michigan}{}{\begin{itemize}%
\item BIOINF 576: Tool Development for Bioinformatics
%
\end{itemize}}
    \cventry{2019-2022}{Facilitator \& Capstone Project Mentor}{Girls Who Code at U-M DCMB}{University of Michigan}{}{\begin{itemize}%
\item Weekly Club during the school year and week-long Summer Experience for high schoolers to learn Python for data science
%
\end{itemize}}
    \cventry{2018-present}{Workshop Instructor \& Helper}{U-M Carpentries}{University of Michigan}{}{\begin{itemize}%
\item 2-day Software Carpentry workshops teaching computational skills for reproducible research
%
\end{itemize}}
    \cventry{Jun 2022}{Instructor}{}{Virtual}{}{\begin{itemize}%
\item Intro to R \& RNA-Seq Workshop for ASM Microbe conference attendees
%
\end{itemize}}
    \cventry{Apr 2019}{DNA Day Ambassador}{Michigan DNA Day}{Pioneer High School, Ann Arbor, MI}{}{\begin{itemize}%
\item Epigenetics \& Scientific Journeys
%
\end{itemize}}
    \cventry{Mar 2019}{Workshop helper}{Graduate Society of Black Engineers and Scientists}{University of Michigan}{}{\begin{itemize}%
\item Data Visualization with Python Workshop
%
\end{itemize}}
    \cventry{Mar 2019}{Capstone Activity Leader}{Females Excelling More in Math, Engineering, \& the Sciences}{University of Michigan}{}{\begin{itemize}%
\item Binary Numbers through Ozobots with GWC at U-M DCMB
%
\end{itemize}}
    \cventry{2012-2018}{Tutor}{freelance}{}{}{\begin{itemize}%
\item for high school and college students in Biology, Calculus, Chemistry, Computer Science, and Bioinformatics.%
\end{itemize}}

\hypertarget{service}{%
\section{Service}\label{service}}

\nopagebreak
    \cventry{2019-present}{Executive Committee Member: Open Source Technical Lead}{Girls Who Code at U-M DCMB}{}{}{\begin{itemize}%
\item Plan, apply for funding, develop curriculum, and maintain resources to teach introductory Python programming \& data science to young women+.%
\item Facilitate collaborative development and maintenance of our open source teaching resources.%
\item Organize our year-round Club and annual Data Science Summer Experience for high school women+.%
\end{itemize}}
    \cventry{2019-present}{Organizer \& Maintainer}{U-M Carpentries}{}{}{\begin{itemize}%
\item Co-lead development \& maintenance of a curriculum for workshops teaching programming skills for reproducible research.%
\item Maintain the website, develop curriculum, and organize workshops.%
\item Collaborate with U-M Women in Science and Engineering to organize workshops for women+.%
\end{itemize}}
    \cventry{2021-present}{Mentor}{Schloss Lab}{}{}{\begin{itemize}%
\item Mentor an undergraduate student in building reproducible machine learning models to predict \_C. difficile\_ infection severity from gut microbiome composition.%
\end{itemize}}
    \cventry{2021-present}{CoderSpaces co-host}{U-M ISR Data Science Hub}{}{}{\begin{itemize}%
\item Hold office hours at a weekly virtual help session for data science practitioners%
\end{itemize}}
    \cventry{2021-present}{Peer reviewer}{}{}{}{\begin{itemize}%
\item PLOS ONE (1)%
\end{itemize}}
    \cventry{2019-2021}{Graduate Student Coordinator}{U-M Data Analysis Networking Group}{}{}{\begin{itemize}%
\item Organize monthly meetings \& a one-day symposium for researchers to sharpen their data analysis skills.%
\item Apply for funding through a Rackham Interdisciplinary Workshop grant.%
\end{itemize}}
    \cventry{2009-present}{Volunteer Sound Engineer}{various churches and non-profit organizations}{}{}{\begin{itemize}%
\item %
\end{itemize}}

\hypertarget{open-source-contributions}{%
\section{Open Source Contributions}\label{open-source-contributions}}

\hypertarget{software}{%
\subsection{Software}\label{software}}

\nopagebreak
    \cventry{}{mikropml}{User-Friendly R Package for Supervised Machine Learning Pipelines}{}{}{\begin{itemize}%
\item Co-author and maintainer%
\end{itemize}}
    \cventry{}{schtools}{Schloss Lab tools for reproducible microbiome research (R package)}{}{}{\begin{itemize}%
\item Co-author and maintainer%
\end{itemize}}
    \cventry{}{mikropml snakemake workflow}{Template for running mikropml with Snakemake}{}{}{\begin{itemize}%
\item Co-author and maintainer%
\end{itemize}}
    \cventry{}{mothur}{Command-Line Tool for Processing 16S rRNA Gene Sequence Data}{}{}{\begin{itemize}%
\item Contributor%
\end{itemize}}
    \cventry{}{mothur snakemake workflow}{Snakemake template for amplicon sequence analysis with mothur}{}{}{\begin{itemize}%
\item Co-author%
\end{itemize}}

\hypertarget{curricula}{%
\subsection{Curricula}\label{curricula}}

\nopagebreak
    \cventry{}{U-M Software Carpentry}{Intro to R- the Unix shell- and git for workshops on reproducible research.}{}{}{\begin{itemize}%
\item Co-author and maintainer%
\end{itemize}}
    \cventry{}{Girls Who Code at U-M DCMB}{Intro to Python for Data Science for Girls Who Code clubs.}{}{}{\begin{itemize}%
\item Co-author and maintainer%
\end{itemize}}
    \cventry{}{Code Clubs}{Short coding tutorials for lab meetings}{}{}{\begin{itemize}%
\item Contributor%
\end{itemize}}
    \cventry{}{U-M DANG!}{repro-packs: Organizing projects for reproducibility and headache prevention.}{}{}{\begin{itemize}%
\item Author%
\end{itemize}}
    \cventry{}{Intro to R \& RNA-seq}{Workshop for 2022 ASM Microbe attendees}{}{}{\begin{itemize}%
\item Contributor%
\end{itemize}}

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

\hypertarget{talks}{%
\subsection{Talks}\label{talks}}

\nopagebreak
    \cventry{Nov 2022}{Bioinformatics Student Research Hour}{Predicting \_C. difficile\_ infection severity from the taxonomic composition of the gut microbiome}{University of Michigan}{}{\empty}
    \cventry{Feb 2022}{Seminar for the KG Jebsen Center for Genetic Epidemiology}{Intro to git \& GitHub}{(Virtual) Norwegian University of Science and Technology}{}{\empty}
    \cventry{Mar 2021}{Bioinformatics Student Research Hour}{OptiFit: a fast method for fitting amplicon sequences to existing OTUs}{(Virtual) University of Michigan}{}{\empty}
    \cventry{Apr 2018}{Systems Biology and Omics Integration Seminar}{Developing a Global Homology Analysis for Comparative Genomics}{University of Kentucky}{}{\empty}

\hypertarget{posters}{%
\subsection{Posters}\label{posters}}

\nopagebreak
    \cventry{Jun 2022}{ASM Microbe}{Predicting the severity of \_C. difficile\_ infections from the taxonomic composition of the gut microbiome}{Washington, DC}{}{\empty}
    \cventry{Jun 2020}{ASM Microbe}{OptiFit: a fast method for fitting amplicon sequences to existing OTUs}{Virtual}{}{\empty}
    \cventry{Apr 2018}{Showcase for Undergraduate Scholars}{Developing a Global Homology Analysis for Comparative Genomics}{University of Kentucky}{}{\empty}
    \cventry{Apr 2018}{National Conference on Undergraduate Research}{Developing a Global Homology Analysis for Comparative Genomics}{University of Central Oklahoma}{}{\empty}
    \cventry{Apr 2016}{Showcase for Undergraduate Scholars}{Processing RNA-seq Reads of Plants Infected with the Coffee Ringspot Virus}{University of Kentucky}{}{\empty}
    \cventry{Apr 2016}{UT-KBRIN Bioinformatics Summit}{Processing RNA-seq Reads of Plants Infected with the Coffee Ringspot Virus}{Cadiz, KY}{}{\empty}
    \cventry{Apr 2015}{Showcase for Undergraduate Scholars}{The Effect of Meditation on Performance}{University of Kentucky}{}{\empty}

\hypertarget{awards}{%
\section{Awards}\label{awards}}

\hypertarget{grants-and-fellowships}{%
\subsection{Grants and Fellowships}\label{grants-and-fellowships}}

\nopagebreak
    \cventry{2022}{Conference Travel Grant}{\$900}{Rackham Graduate School <br> University of Michigan}{}{\empty}
    \cventry{2020-2021}{Rackham Interdisciplinary Workshop Grant}{\$500}{Rackham Graduate School <br> University of Michigan}{}{\empty}
    \cventry{2020}{Conference Travel Grant}{\$800}{Rackham Graduate School <br> University of Michigan}{}{\empty}
    \cventry{2019-2020}{Rackham Interdisciplinary Workshop Grant}{\$500}{Rackham Graduate School <br> University of Michigan}{}{\empty}
    \cventry{2019-2021}{NIH T32 Bioinformatics Training Program Fellow}{}{Bioinformatics Graduate Program <br> University of Michigan}{}{\empty}
    \cventry{2017}{Oswald Research \& Creativity Award <br> 2nd place in Biological Sciences}{\$200}{Office of Undergraduate Research <br> University of Kentucky}{}{\empty}
    \cventry{2017}{Summer Research Grant}{\$2,000}{Office of Undergraduate Research <br> University of Kentucky}{}{\empty}
    \cventry{2014-2018}{Presidential Scholarship}{out-of-state full tuition}{University of Kentucky}{}{\empty}

\hypertarget{honors}{%
\subsection{Honors}\label{honors}}

\nopagebreak
    \cventry{2018}{Graduated Cum Laude with Departmental Honors in Biology}{}{University of Kentucky}{}{\empty}
    \cventry{2018}{Biology Undergraduate Research Award Nominee}{}{University of Kentucky}{}{\empty}
    \cventry{2014-2018}{Lewis Honors College}{}{University of Kentucky}{}{\empty}

\hypertarget{continuing-education}{%
\section{Continuing Education}\label{continuing-education}}

\nopagebreak
    \cventry{Jan 2020}{Building Tidy Tools workshop at rstudio::conf}{Rstudio, PBC}{San Francisco, CA}{}{\empty}
    \cventry{Dec 2019}{Winter School in Research Software Engineering}{US Research Software Sustainability Institute}{Seattle, WA}{}{\empty}
    \cventry{Jun 2019}{Software Carpentry Instructor Training}{The Carpentries}{University of Michigan}{}{\empty}
    \cventry{May 2019}{PyCon Education Summit \& Conference}{The Python Software Foundation}{Cleveland, OH}{}{\empty}
    \cventry{Apr 2019}{MICROBIOL 612.2}{Riffomonas Minimal R Workshop}{University of Michigan}{}{\empty}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\textbf{*} Indicates co-first author

begin\{itemize\} \newline  

\item

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{8}
\tightlist
\item
  Armour CR, \textbf{Sovacool KL}, Close WL, Topçuoğlu BD, Wiens J,
  Schloss PD. Sep 2022. Streamlined implementation of a machine learning
  model to classify screen relevant neoplasia using reference-based OTU
  clustering. \emph{bioRxiv}.
  \href{https://doi.org/10.1101/2022.09.01.506299}{10.1101/2022.09.01.506299}
  \newline  

  \item

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \setcounter{enumii}{7}
  \tightlist
  \item
    Barron MR, \textbf{Sovacool KL}, Abernathy-Close L, Vendrov KC,
    Standke AK, Bergin IL, Schloss PD, Young VB. Jul 2022. Intestinal
    Inflammation Reversibly Alters the Microbiota to Drive
    Susceptibility to Clostridioides Difficile Colonization in a Mouse
    Model of Colitis. \emph{mBio}.
    \href{https://doi.org/10.1128/mbio.01904-22}{10.1128/mbio.01904-22}
    \newline  

    \item

    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \setcounter{enumiii}{6}
    \tightlist
    \item
      \textbf{Sovacool KL}, Westcott SL, Mumphrey MB, Dotson GA, Schloss
      PD. Feb 2022. OptiFit: An Improved Method for Fitting Amplicon
      Sequences to Existing OTUs. \emph{mSphere}.
      \href{https://doi.org/10.1128/msphere.00916-21}{10.1128/msphere.00916-21}
      \newline  

      \item

      \begin{enumerate}
      \def\labelenumiv{\arabic{enumiv}.}
      \setcounter{enumiv}{5}
      \tightlist
      \item
        *Lapp Z, \textbf{*Sovacool KL}, Lesniak N, King D, Barnier C,
        Flickinger M, Krüger J, Armour CR, Lapp MM, Tallant J, Diao R,
        Oneka M, Tomkovich S, Anderson JM, Lucas SK, Schloss PD. Jan
        2022. Developing and Deploying an Integrated Workshop Curriculum
        Teaching Computational Skills for Reproducible Research.
        \emph{JOSE}.
        \href{https://doi.org/10.21105/jose.00144}{10.21105/jose.00144}
        \newline  

        \item

        \begin{enumerate}
        \def\labelenumv{\arabic{enumv}.}
        \tightlist
        \item
          *Duda M, \textbf{*Sovacool KL}, Farzaneh N, Nguyen VK, Haynes
          SE, Falk H, Furman KL, Walker LA, Diao R, Oneka M, Drotos AC,
          Woloshin A, Dotson GA, Kriebel A, Meng L, Thiede SN, Lapp Z,
          Wolford BN. Dec 2021. Teaching Python for Data Science:
          Collaborative Development of a Modular \& Interactive
          Curriculum. \emph{JOSE}.
          \href{https://doi.org/10.21105/jose.00138}{10.21105/jose.00138}
          \newline  

          \item

          \begin{enumerate}
          \def\labelenumvi{\arabic{enumvi}.}
          \tightlist
          \item
            *Topçuoğlu BD, *Lapp Z, \textbf{*Sovacool KL}, Snitkin E,
            Wiens J, Schloss PD. May 2021. Mikropml: User-Friendly R
            Package for Supervised Machine Learning Pipelines.
            \emph{JOSS}.
            \href{https://doi.org/10.21105/joss.03073}{10.21105/joss.03073}
            \newline  

            \item

            \begin{enumerate}
            \def\labelenumvii{\arabic{enumvii}.}
            \tightlist
            \item
              Everson KM, Gray LN, Jones AG, Lawrence NM, Foley ME,
              \textbf{Sovacool KL}, Kratovil JD, Hotaling S, Hime PM,
              Storfer A, Parra-Olea G, Percino-Daniel R, Aguilar-Miguel
              X, O'Neill EM, Zambrano L, Shaffer HB, Weisrock DW. Apr
              2021. Geography Is More Important than Life History in the
              Recent Diversification of the Tiger Salamander Complex.
              \emph{PNAS}.
              \href{https://doi.org/10.1073/pnas.2014719118}{10.1073/pnas.2014719118}
              \newline  

              \item

              \begin{enumerate}
              \def\labelenumviii{\arabic{enumviii}.}
              \tightlist
              \item
                Hagan AK, Lesniak NA, Balunas MJ, Bishop L, Close WL,
                Doherty MD, Elmore AG, Flynn KJ, Hannigan GD, Koumpouras
                CC, Jenior ML, Kozik AJ, McBride K, Rifkin SB, Stough J,
                \textbf{Sovacool KL}, Sze MA, Tomkovich S, Topcuoglu BD,
                Schloss PD. Aug 2020. Ten Simple Rules to Increase
                Computational Skills among Biologists with Code Clubs.
                \emph{PLoS Comput Biol}.
                \href{https://doi.org/10.1371/journal.pcbi.1008119}{10.1371/journal.pcbi.1008119}
                \newline  

                \item

                \begin{enumerate}
                \def\labelenumix{\arabic{enumix}.}
                \tightlist
                \item
                  Goodin MM, Farman M, Inocencio H, Jang C, Jaromczyk
                  JW, Moore N, \textbf{Sovacool KL}. Aug 2016.
                  Processing RNA-Seq Data of Plants Infected with Coffee
                  Ringspot Virus. \emph{BMC Bioinform}.
                  \href{https://doi.org/10.1186/s12859-016-1154-y}{10.1186/s12859-016-1154-y}
                  \newline  end\{itemize\}
                \end{enumerate}
              \end{enumerate}
            \end{enumerate}
          \end{enumerate}
        \end{enumerate}
      \end{enumerate}
    \end{enumerate}
  \end{enumerate}
\end{enumerate}


\end{document}

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
