%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 8 February 2019
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,]{moderncv}

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{HTML}{3873B3}% custom
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\usepackage[]{sans}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\def\donothing#1{#1}
\def\emaillink#1{#1}

%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75,footskip=60pt]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...


\moderncvcolor{black}

% personal data
\name{Kelly}{Sovacool}
\title{PhD Candidate}
\address{University of Michigan}{}{}
 % Phone number
\email{\donothing{\href{mailto:sovacool@umich.edu}{\nolinkurl{sovacool@umich.edu}}}}
\homepage{sovacool.dev} % Personal website
\social[linkedin]{kelly-sovacool}
\social[twitter]{kelly\_sovacool}
\social[github]{kelly-sovacool}
% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted




% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle



\hypertarget{education}{%
\section{Education}\label{education}}

\nopagebreak
    \cventry{2018-present}{PhD Bioinformatics}{Dept. of Computational Medicine and Bioinformatics}{University of Michigan}{}{\begin{itemize}%
\item Advisor: Patrick D. Schloss%
\end{itemize}}
    \cventry{2014-2018}{BS Biology}{Dept. of Biology}{University of Kentucky}{}{\begin{itemize}%
\item Minor: Computer Science%
\end{itemize}}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

TODO: get italics to work inside entries

\nopagebreak
    \cventry{2019-present}{Graduate Student Researcher}{Schloss Lab,  Dept. of Microbiology and Immunology}{University of Michigan}{}{\begin{itemize}%
\item Develop and benchmark bioinformatics pipelines and software for microbial ecology.%
\item Analyze 16S rRNA gene amplicon sequence data.%
\item Apply machine learning methods to gut microbiome classification problems in colorectal cancer and _C. difficile_ infection.%
\item Collaborate with other scientists on microbiome projects and mentor junior lab members.%
\end{itemize}}
    \cventry{2018-2019}{Rotation Student Researcher}{Program in Biomedical Sciences}{University of Michigan}{}{\begin{itemize}%
\item %
\end{itemize}}
    \cventry{2015-2018}{Undergraduate Lab Assistant}{Moseley Bioinformatics Lab,  Dept. of Molecular and Cellular Biochemistry}{University of Kentucky}{}{\begin{itemize}%
\item Developed a computational tool in Python for identifying sets of orthologous and paralogous gene products in whole genomes to facilitate collinearity analysis and detection of gene duplication events.%
\end{itemize}}
    \cventry{2016-2018}{BIO395 Independent Research Student}{Weisrock Lab,  Dept. of Biology}{University of Kentucky}{}{\begin{itemize}%
\item Developed bash scripts and a SNP calling pipeline in Snakemake.%
\item Population structure analysis of the _Ambystoma tigrinum_ species complex.%
\item Bayesian species delimitation of the _Desmognathus fuscus_ species complex.%
\end{itemize}}
    \cventry{2015-2016}{Undergraduate Lab Assistant}{Jaromczyk Lab,  Dept. of Computer Science}{University of Kentucky}{}{\begin{itemize}%
\item Maintained the _Epichloë festucae_ genome project database.%
\item Analyzed RNA-seq data of _Chenopodium quinoa_ and coffee ringspot virus.%
\end{itemize}}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\nopagebreak
    \cventry{Jan-Apr 2023}{Graduate Student Instructor}{Dept. of Computational Medicine \& Bioinformatics}{University of Michigan}{}{\begin{itemize}%
\item BIOINF 576: Tool Development for Bioinformatics
%
\end{itemize}}
    \cventry{2019-2022}{Facilitator \& Capstone Project Mentor}{Girls Who Code at U-M DCMB}{University of Michigan}{}{\begin{itemize}%
\item Weekly Club during the school year and week-long Summer Experience for high schoolers to learn Python for data science
%
\end{itemize}}
    \cventry{2018-present}{Workshop Instructor \& Helper}{U-M Carpentries}{University of Michigan}{}{\begin{itemize}%
\item 2-day Software Carpentry workshops teaching computational skills for reproducible research
%
\end{itemize}}
    \cventry{Jun 2022}{Instructor}{}{Virtual}{}{\begin{itemize}%
\item Intro to R \& RNA-Seq Workshop for ASM Microbe conference attendees
%
\end{itemize}}
    \cventry{Apr 2019}{DNA Day Ambassador}{Michigan DNA Day}{Pioneer High School, Ann Arbor, MI}{}{\begin{itemize}%
\item Epigenetics \& Scientific Journeys
%
\end{itemize}}
    \cventry{Mar 2019}{Workshop helper}{Graduate Society of Black Engineers and Scientists}{University of Michigan}{}{\begin{itemize}%
\item Data Visualization with Python Workshop
%
\end{itemize}}
    \cventry{Mar 2019}{Capstone Activity Leader}{Females Excelling More in Math, Engineering, \& the Sciences}{University of Michigan}{}{\begin{itemize}%
\item Binary Numbers through Ozobots with GWC at U-M DCMB
%
\end{itemize}}
    \cventry{2012-2018}{Tutor}{freelance}{}{}{\begin{itemize}%
\item for high school and college students in Biology, Calculus, Chemistry, Computer Science, and Bioinformatics.%
\end{itemize}}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\textbf{*} Indicates co-first author

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-goodin_processing_2016}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Goodin, M. M., Farman, M., Inocencio, H., Jang, C.,
Jaromczyk, J. W., Moore, N., \& Sovacool, K. L. (2016, August).
Processing RNA-Seq data of plants infected with coffee ringspot virus.
\emph{Proceedings of the 15th Annual UT-KBRIN Bioinformatics Summit
2016: Cadiz, KY, USA. 8-10 April 2016}.
\url{https://doi.org/10.1186/s12859-016-1154-y}}

\leavevmode\vadjust pre{\hypertarget{ref-hagan_ten_2020}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Hagan, A. K., Lesniak, N. A., Balunas, M. J., Bishop,
L., Close, W. L., Doherty, M. D., Elmore, A. G., Flynn, K. J., Hannigan,
G. D., Koumpouras, C. C., Jenior, M. L., Kozik, A. J., McBride, K.,
Rifkin, S. B., Stough, J. M. A., Sovacool, K. L., Sze, M. A., Tomkovich,
S., Topcuoglu, B. D., \& Schloss, P. D. (2020). Ten simple rules to
increase computational skills among biologists with Code Clubs.
\emph{PLoS Comput Biol}, \emph{16}(8), e1008119.
\url{https://doi.org/10.1371/journal.pcbi.1008119}}

\leavevmode\vadjust pre{\hypertarget{ref-everson_geography_2021}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Everson, K. M., Gray, L. N., Jones, A. G., Lawrence, N.
M., Foley, M. E., Sovacool, K. L., Kratovil, J. D., Hotaling, S., Hime,
P. M., Storfer, A., Parra-Olea, G., Percino-Daniel, R., Aguilar-Miguel,
X., O'Neill, E. M., Zambrano, L., Shaffer, H. B., \& Weisrock, D. W.
(2021). Geography is more important than life history in the recent
diversification of the tiger salamander complex. \emph{PNAS},
\emph{118}(17). \url{https://doi.org/10.1073/pnas.2014719118}}

\leavevmode\vadjust pre{\hypertarget{ref-topcuoglu_mikropml_2021}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{*Topçuoğlu, B. D., *Lapp, Z., *Sovacool, K. L., Snitkin,
E., Wiens, J., \& Schloss, P. D. (2021). Mikropml: User-Friendly R
Package for Supervised Machine Learning Pipelines. \emph{JOSS},
\emph{6}(61), 3073. \url{https://doi.org/10.21105/joss.03073}}

\leavevmode\vadjust pre{\hypertarget{ref-duda_teaching_2021}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{*Duda, M., *Sovacool, K. L., Farzaneh, N., Nguyen, V.
K., Haynes, S. E., Falk, H., Furman, K. L., Walker, L. A., Diao, R.,
Oneka, M., Drotos, A. C., Woloshin, A., Dotson, G. A., Kriebel, A.,
Meng, L., Thiede, S. N., Lapp, Z., \& Wolford, B. N. (2021). Teaching
Python for Data Science: Collaborative development of a modular \&
interactive curriculum. \emph{JOSE}, \emph{4}(46), 138.
\url{https://doi.org/10.21105/jose.00138}}

\leavevmode\vadjust pre{\hypertarget{ref-lapp_developing_2022}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{*Lapp, Z., *Sovacool, K. L., Lesniak, N., King, D.,
Barnier, C., Flickinger, M., Krüger, J., Armour, C. R., Lapp, M. M.,
Tallant, J., Diao, R., Oneka, M., Tomkovich, S., Anderson, J. M., Lucas,
S. K., \& Schloss, P. D. (2022). Developing and deploying an integrated
workshop curriculum teaching computational skills for reproducible
research. \emph{JOSE}. \url{https://doi.org/10.21105/jose.00144}}

\leavevmode\vadjust pre{\hypertarget{ref-sovacool_optifit_2022}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Sovacool, K. L., Westcott, S. L., Mumphrey, M. B.,
Dotson, G. A., \& Schloss, P. D. (2022). OptiFit: An Improved Method for
Fitting Amplicon Sequences to Existing OTUs. \emph{mSphere}.
\url{https://doi.org/10.1128/msphere.00916-21}
\CSLBlock{1752 N St., N.W., Washington, DC}}

\leavevmode\vadjust pre{\hypertarget{ref-barron_intestinal_2022}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Barron, M. R., Sovacool, K. L., Abernathy-Close, L.,
Vendrov, K. C., Standke, A. K., Bergin, I. L., Schloss, P. D., \& Young,
V. B. (2022). Intestinal Inflammation Reversibly Alters the Microbiota
to Drive Susceptibility to Clostridioides difficile Colonization in a
Mouse Model of Colitis. \emph{mBio}, \emph{0}(0), e01904--22.
\url{https://doi.org/10.1128/mbio.01904-22}}

\leavevmode\vadjust pre{\hypertarget{ref-armour_streamlined_2022}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Armour, C. R., Sovacool, K. L., Close, W. L., Topçuoğlu,
B. D., Wiens, J., \& Schloss, P. D. (2022). Streamlined implementation
of a machine learning model to classify screen relevant neoplasia using
reference-based OTU clustering. \emph{bioRxiv}.
\url{https://doi.org/10.1101/2022.09.01.506299}}


\end{document}

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
